Thread Pool in GeckoDB/BOLSTER - Implementing a Thread Pool for a high performance Database System \\

### 2018-06-26 Presentations/Paper/paper_thread_pool.tex
Enhance Setup section paper

\section{Experimental Environment}	
In this section, we present our experimental environment focussing on the design of our benchmarks and the system configuration we used to evaluate our thread pool implementation.

@@

\subsection{Experimental Configuration}
\textbf{TODO: Change!}\\The operating system is Ubuntu 17.04 with linux kernel version 4.13 running in a virtual machine on an Intel Core i7-6700HQ, 4x 2.6 GHz (Skylake) and 8GB DDR3 RAM running on 1600Mhz. We reduce the number of cores of the virtual machine to 4 instead of 8 virtual cores of the CPU. The CPU has 256KB L1 cache, 1MB L2 cache, and 6MB L3 cache. All simulations are repeated three times and a median value of all repetitions is used for evaluation.

>>>>

\section{Experimental Environment}	
In this section, we present our experimental environment focusing on the design of our benchmarks and the system configuration we used to evaluate our thread pool implementation.

@@

\subsection{Experimental Configuration}
%\textbf{TODO: Change!}\\The operating system is Ubuntu 17.04 with linux kernel
%version 4.13 running in a virtual machine on an Intel Core i7-6700HQ, 4x 2.6 GHz
%(Skylake) and 8GB DDR3 RAM running on 1600Mhz. We reduce the number of cores of
%the virtual machine to 4 instead of 8 virtual cores of the CPU. The CPU has
%256KB L1 cache, 1MB L2 cache, and 6MB L3 cache. All benchmarks have been
%repeated three times and a median value of all repetitions is being used for evaluation.

For testing purposes we used primarly Linux setups, for one Ubuntu 17.04
(linux 4.13) in an virtual machine environment, second Archlinux (linux
4.17.2-1) running native, both updated on stable branch. Tests have also been
conducted on Windows 10 and macOs HighSierra machines.

In our setups mostly Sky- and Kabylake processors have been used with memory
ranging from 8 to 24 GB of both DDR3-SODIMM and DDR4-SODIMM.

All benchmarks have been repeated three times and a median value of all
repetitions is being used for evaluation.
